---
title: "Case Study"
output: html_document
---

Today we're studying a case.

```{r, include = FALSE,message=FALSE,warning=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

## Get Data

```{r}
library(p8105.datasets)

data(nyc_airbnb)
```



## Brainstorm questions

* what variables are relevant to higher reviews/scores?

* what are the popular places to rent?


```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, neighbourhood) %>% 
  distinct() %>% 
  summarize (
  mean_review_location = mean(review_scores_location, na.rm = TRUE)
  ) %>% 
  arrange(desc(mean_review_location))
```

* what portion of locations are private rooms / entire apartments?


* what variables are relevant to higher price?
```{r}
nyc_airbnb %>% 
  group_by(neighbourhood_group, room_type) %>% 
  summarize (mean_price = mean(price, na.rm = TRUE)) %>% 
    pivot_wider(
      names_from = room_type,
      values_from = mean_price
  ) 
```

```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", room_type == "Entire home/apt",
  price > 1000) %>% 
  ggplot(aes(x = price)) +
  geom_histogram()
```

price vs. rating?
```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  ggplot(aes(x = "stars", y = "price")) +
  geom_point() +
  facet_grid(. ~ room_type)
```

somewhat fancy plot
```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  group_by(neighbourhood) %>% 
  summarize(mean_price = mean(price, na.rm = TRUE)) %>% 
  arrange(desc(mean_price))
```


```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  filter(price <= 1000) %>% 
  mutate(neighbourhood = fct_reorder(neighbourhood, price)) %>% 
  ggplot(aes(x = neighbourhood, y = price)) +
  geom_boxplot() +
  coord_flip()
```


price vs. location psuedo map
```{r}
nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan") %>% 
  filter(price <= 1000) %>% 
  sample_n(1000) %>% 
  ggplot(aes(x = lat, y = long, color = price)) + geom_point()
```

! price vs. location real map using leaflet
```{r}
library(leaflet)
pal <- colorNumeric("viridis", domain = c(0, 1000))

nyc_airbnb %>% 
  filter(neighbourhood_group == "Manhattan", room_type == "Entire home/apt") %>% 
  filter(price <= 1000) %>% 
  sample_n(1000) %>% 
  leaflet() %>% 
  addProviderTiles(providers$CartoDB.Positron) %>% 
  addCircleMarkers(~lat, ~long, radius = 0.5, color = ~pal(price))
```

